---
title: ""
output:
  html_document:
    includes:
      in_header: hero-image.html
---

‘Networking Archives’ was a three-year, [AHRC funded](https://gtr.ukri.org/projects?ref=AH%2FR014817%2F1) research project which merged the early modern correspondence data collected in ‘Early Modern Letters Online’ with metadata from the ‘Gale State Papers Online’ to create the UK’s largest meta-archive of curated early modern correspondence metadata. 

This site archives the project's tools, research, and resources. It includes a number of [tools](https://networkingarchives.github.io/tools.html) which can be used to analyse or browse the project's correspondence data. You can find extensive [teaching materials](https://networkingarchives.github.io/curriculum.html) which can be freely re-used, including an [interactive glossary](https://networkingarchives.shinyapps.io/interactive_glossary/){target="_blank"} of network terms. See the project's [Github page](https://github.com/networkingarchives){target="_blank"} for source code and (when ready) the datasets. 

Use the menu above (or click on the nodes in the network diagram below) to navigate the site.

```{r echo=FALSE, message=FALSE, warning=FALSE}

library(visNetwork)
library(tidyverse)
library(igraph)
library(ggraph)
library(tidygraph)

```

```{r echo=FALSE,smessage=FALSE, warning=FALSE, fig.width=8}

# g = read_csv('../../GitHub/Book-Chapters/data/universal_network.csv') %>% 
#   filter(source == 'stuart') %>% distinct(X1, X2) %>%
#   graph_from_data_frame() %>% 
#   as_tbl_graph() %>% 
#   mutate(degree = centrality_degree()) %>% 
#   filter(degree > 200) %>% 
#   mutate(size = sqrt(degree)) %>% left_join(read_csv('../../GitHub/Book-Chapters/data/universal_people.csv')) %>% 
#   mutate(name = main_name) %>% mutate(color.border = 'rgba(0,0,0,.5') %>% mutate(color.alpha = .8) %>% mutate(color.background = 'rgba(0,0,255,.5') 
# 
# visIgraph(g, physics = T, layout = "layout_nicely")


site_g = tibble(from = c('Networking Archives', 
                         'Networking Archives',
                         'Networking Archives',
                         'Networking Archives',
                         'Networking Archives',
                       'About',
                       'About',
                       'About',
                       'Research',
                       'Research', 
                       'Tools & Training', 
                       'Tools & Training', 
                       'Tools & Training', 
                       'Tools & Training'), 
                to = c('About', 
                       'Research', 
                       'Tools & Training', 
                       "News & Blog", 
                       'Contact',
                       'Team',
                       'Partners',
                       'Credits',
                       'Research Agenda',
                       'Publications',
                       'Curriculum',
                       'Training Schools',
                       'Tools',
                       'Interactive Glossary')) %>% 
  graph_from_data_frame() %>% 
  as_tbl_graph() %>% 
  mutate(title = name) %>% 
  mutate(size = c(5,3,3,3,3,1,1,1,1,1,1,1,1,1,1)*10) %>% 
  mutate(color.background = c('blue', 'red', 'red', 'red', 'red', 'green', 'green', 'green', 'green', 'green', 'green', 'green', 'green', 'green', 'green')) %>% 
  mutate(color.background = 'lightblue') %>% 
  mutate(color.border = 'black') %>% 
  mutate(font.color = 'black') %>% 
  mutate(size = 20) %>% 
  mutate(shape = 'circle') %>% 
  mutate(url = c('https://networkingarchives.github.io',
                 'https://networkingarchives.github.io/about.html',
                 'https://networkingarchives.github.io/research.html',
                 'https://networkingarchives.github.io/tools.html',
                 'https://networkingarchives.github.io/blog',
                 'https://networkingarchives.github.io/contact.html',
                 'https://networkingarchives.github.io/team.html',
                 'https://networkingarchives.github.io/partners.html',
                 'https://networkingarchives.github.io/credits.html',
                 'https://networkingarchives.github.io/research.html',
                 'https://networkingarchives.github.io/publications.html',
                 'https://networkingarchives.github.io/curriculum.html',
                 'https://networkingarchives.github.io/training.html',
                 'https://networkingarchives.github.io/tools.html',
                 'https://networkingarchives.shinyapps.io/interactive_glossary/')) %>% 
  activate(edges) %>%
  mutate(color = 'black')

visIgraph(site_g, physics = T, layout = "layout_nicely") %>% 
            visEvents(click = 
                          "function(params) {
    var nodeID = params.nodes[0];
    var url = this.body.nodes[nodeID].options.url;
    window.open(url, '_self');
   }")
  
```

